---
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: false
    keep_tex: true
    includes:
      in_header: "sipreamble.tex"
    extra_dependencies: ["float"]
bibliography: "references.bib"
title: Supporting Information for "A genetics-style document using RMarkdown"
author:
  - Aaron P. Ragsdale
date:
  - \today
---

```{r sisetup, echo=F}
options(tinytex.clean = FALSE)
```

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{equation}{0}

# The diffusion equation and moment system for the two-locus sampling distribution

The two-locus diffusion equation with additive selection was first described by
@Kimura1955-qe and studied extensively in the 1960s and 70s [e.g., @Ohta1969-ie].

\clearpage
\newpage

# Supplementary Tables

```{r 1kgpops, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
pops <- read.csv("tables/populations.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(pops, "latex", booktabs=T,
    caption="Thousand Genomes Project population descriptions for populations used in this study.") %>%
kable_styling(latex_options = "HOLD_position")
```

```{r msldfe, echo=F, tab.align="center"}
library(knitr)
library(kableExtra)
dfes <- read.csv("tables/msl_dfes.txt", sep=";", header=TRUE, check.names=FALSE)
knitr::kable(dfes, "latex", booktabs=T, escape=FALSE,
    linesep = c("", "", "\\addlinespace"),
    caption="DFEs inferred for missense and loss-of-function variants in MSL for varying values of $h$. General patterns are consistent across different chosen values of $h$, although $h=0$ results in poorer fits for both missense and LOF variants. Columns to the right of the log-likelihood (LL) column show proportions of new mutations with $|s|$ in each given bin.") %>%
kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\clearpage
\newpage

# Supplementary Figures

```{r fig2, echo=F, fig.cap="(ref:figS1)", fig.align="center"}
knitr::include_graphics("figures/fig2.pdf")
```

(ref:figS1) The distribution at stationarity of AB haplotype counts in a
sample size of 30, in which we observe 10 $A$ alleles at the left locus, and 10
$B$ alleles at the right locus.

\clearpage
\newpage

# References
